Quotients of the magmatic operad:\\ lattice structures and convergent rewrite systems

### 2018-09-11 Mag_quotients.tex
MAJ

Finally, for every integer $\gamma\geq 2$, we define the
\Def{$\gamma$-right comb operad} $\RC{\gamma}$ as follows. For every
arity $n$, we let
\begin{equation}
  \RC{\gamma}(n):=
    \begin{cases}
        \As(n) &
        \mbox{if } n \leq \gamma-1, \\
        \RComb{n}
            & \mbox{otherwise},
    \end{cases}
\end{equation}
and the partial composition $\Tfr_1 \circ_i \Tfr_2$ is the partial
composition of $\Tfr_1$ and $\Tfr_2$ in $\Mag$ if the integer
\begin{math}
  n:=|\Tfr_1|+|\Tfr_2| 
\end{math}
is strictly smaller than $\gamma$, and $\RComb{n}$, otherwise.
\medbreak

\begin{Lemma}
  \label{lem:presentation_of_RC}
  We have
  \begin{equation}
  \label{equ:presentation_of_RC}
  \NiHil:=\KMag/_{\IRCC{\gamma}}
  \end{equation}
  where $\IRC{\gamma}$ is the ideal spanned by the elements
  $\Tfr-\RComb{\gamma}$, where $\Tfr$ runs over all the trees of arity
  $\gamma$.
\end{Lemma}

\begin{proof}
  \Todo{todo}
\end{proof}

>>>>

Finally, for every integer $\gamma\geq 2$, we define the
\Def{$\gamma$-right comb operad} $\RC{\gamma}$ as follows. For every
arity $n$, we let
\begin{equation}
  \label{equ:compositions_of_RC}
  \RC{\gamma}(n):=
    \begin{cases}
        \As(n) &
        \mbox{if } n \leq \gamma, \\
        \RComb{n}
            & \mbox{otherwise},
    \end{cases}
\end{equation}
and the partial composition $\Tfr_1 \circ_i \Tfr_2$ is the partial
composition of $\Tfr_1$ and $\Tfr_2$ in $\Mag$ if the integer
\begin{math}
  n:=|\Tfr_1|+|\Tfr_2| 
\end{math}
is strictly smaller than $\gamma$, and $\RComb{n}$, otherwise.
\medbreak

\begin{Lemma}
  \label{lem:presentation_of_RC}
  We have an isomorphism
  \begin{equation}
  \label{equ:presentation_of_RC}
  \RC{\gamma}\simeq\KMag/_{\IRCC{\gamma}}
  \end{equation}
  where $\IRCC{\gamma}$ is the ideal spanned by the elements
  $\Tfr-\RComb{\gamma}$, where $\Tfr$ runs over all the binary trees of
  arity $\gamma+1$. In other words, $\RC{\gamma}$ is a combinatorial
  realization of
  \begin{math}
    \KMag/_{\IRCC{\gamma}}.
    \end{math}
\end{Lemma}

\begin{proof}
  Let $R^{(\gamma)}$ be the set of rewrite rules
  $\Tfr\Rew\RComb{\gamma}$, where $\Tfr$ runs over all the binary trees
  of arity $\gamma+1$ different from $\RComb{\gamma}$. The unique normal
  form of arity $n\geq\gamma+1$ for  $R^{(\gamma)}$ is equal to
  $\RComb{n}$, so that $R^{(\gamma)}$ is a convergent presentation of
  \begin{math}
    \KMag/_{\IRC{\gamma}}.
  \end{math}
  Moreover, the normal forms of arity $n\leq\gamma$ are all the trees of
  arity $n$ and, by using the convergent presentation
  $R^{(\gamma)}$, we see that the compositions of
  \begin{math}
    \KMag/_{\IRC{\gamma}}
  \end{math}
  satisfy~\eqref{equ:compositions_of_RC}. Hence, $R^{(\gamma)}$ is also a
  convergent presentation of
  \begin{math}
    \RC{\gamma}
  \end{math}
  which proves Lemma~\ref{lem:presentation_of_RC}.
\end{proof}
